A longitudinal analysis of the social information in infants' naturalistic

### 2022-07-19 paper/manuscript/appendix.Rmd
last edits to figures/ms in first stage of proofs

## A3 Location of OpenPose False Positives
Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
Qualitatively, the location of these false positives do not look much different than the true positive detections.

```{r density-op-fps, fig.width=6.5, fig.height=3.2, fig.cap="Density plot of the locations of false positives for OpenPose detections for faces (left) and hands (right) in the gold set."}
load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=top+0.5*height) %>% 
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=10) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=top+0.5*height) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=10) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

@@

ggsave('figs_publication_final/figurea8_activities_by_location.pdf', width = 7.2 , height = 4)

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
# single location videos
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave('figs_publication_final/figurea8b_activities_by_single_location.pdf', width = 7.2, height = 4)

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
# normalize by location
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
  group_by(Activity, Location) %>%
  summarise(n = n(),
            prop_loc = n / loc_freq) %>% 
  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

>>>>

## A3 Location of OpenPose False Positives

```{r}
load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))

ddd <- gold_sample_all_dets %>%  # has bounding box info
  left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan)) %>%
    mutate(x=left+0.5*width, y=top+0.5*height)  # gold_sample has manual annotations merged

fp_faces <-  ddd %>% 
  filter(face_eval_ketan=="F", label=="face")

fp_hands <-  ddd %>% 
  filter(hand_eval_ketan=="FP", label=="hand") 
```

Below we visualize the locations of the `r length(fp_faces)` faces in `r length(unique(fp_faces$frame))` frames that OpenPose detected in the gold set frames that were not actually there, as well as the `r length(fp_hands)`  OpenPose false positive hands (in `r length(unique(fp_hands$frame))` frames) from the gold set.
The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
Qualitatively, the location of these false positives do not look much different than the true positive detections.

```{r density-op-fps, fig.width=6.5, fig.height=3.2, fig.cap="Density plot of the locations of false positives for OpenPose detections for faces (left) and hands (right) in the gold set."}

# density plot of OP's false positive face/hand locations
p1 <- fp_faces %>%
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=10) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

p2 <- fp_hands %>%
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=10) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

@@

# ggsave('figs_publication_final/figurea8_activities_by_location.pdf', width = 7.2 , height = 4)

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
# single location videos
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme_few(base_size=10) +
  scale_fill_continuous(name = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave('figs_publication_final/figurea8a_activities_by_single_location.pdf', width = 7.2, height = 4)

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
# normalize by location
loc_freq_out = loc_freq
meta_long_1loc %>% 
  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
  group_by(Activity, Location) %>%
  summarise(n = n(),
            prop_loc = n / loc_freq) %>% 
  mutate(Location = factor(Location, levels=names(loc_freq_out))) %>%
  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
  geom_tile() +
  theme_few(base_size=10) +
  scale_fill_continuous(name = "Prob.") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

### 2022-07-19 paper/manuscript/manuscript_july2022_apa_final.Rmd
last edits to figures/ms in first stage of proofs

Finally, we also examined whether there were changes in where faces tended to appear in the camera's (and hence, by proxy, the child's) field of view. 
As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure A9 for average density distributions). 
However, we also found evidence that older children tended to see more faces in more variable positions than younger children. 
Specifically, we examined how variable the horizontal and vertical coordinates were of the faces in the infant view. 
To do so, we calculated the coefficient of variation of the horizontal (x) and vertical (y) positions of centers of the faces detected by OpenPose (see Figure \ref{fig:faceDetailed}B), and examined changes across age. 
Faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B, Main effect of position type on variability, B = `r round(x_vs_y_summary$coefficients,4)[3,1]`, SE = `r round(x_vs_y_summary$coefficients,4)[3,2]`, df = `r round(x_vs_y_summary$coefficients,4)[3,3]`, t = `r round(x_vs_y_summary$coefficients,4)[3,4]`, P = `r round(x_vs_y_summary$coefficients,4)[3,5]`).
We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B), (Main effect of age of horizontal position, B = `r round(x_pos_summary$coefficients,4)[2,1]`, SE = `r round(x_pos_summary$coefficients,4)[2,2]`, df = `r round(x_pos_summary$coefficients,4)[2,3]`, t = `r round(x_pos_summary$coefficients,4)[2,4]`, P = `r round(x_pos_summary$coefficients,4)[2,5]`; No main effect of age on vertical position, Main effect of age of horizontal position, B = `r round(y_pos_summary$coefficients,4)[2,1]`, SE = `r round(y_pos_summary$coefficients,4)[2,2]`, df = `r round(y_pos_summary$coefficients,4)[2,3]`, t = `r round(y_pos_summary$coefficients,4)[2,4]`, P = `r round(y_pos_summary$coefficients,4)[2,5]`; )

@@

An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7) and between individual children. 
Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 
This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. 
Each of these positions offer the child differing degrees of visual access to faces and hands. 
While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

>>>>

Finally, we also examined whether there were changes in where faces tended to appear in the camera's (and hence, by proxy, the child's) field of view. 
As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure A9 for average density distributions). 
However, we also found evidence that older children tended to see more faces in more variable positions than younger children. 
Specifically, we examined how variable the horizontal and vertical coordinates were of the faces in the infant view. 
To do so, we calculated the coefficient of variation of the horizontal (x) and vertical (y) positions of centers of the faces detected by OpenPose (see Figure \ref{fig:faceDetailed}B), and examined changes across age. 
Faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B, Main effect of position type on variability, B = `r round(x_vs_y_summary$coefficients,4)[3,1]`, SE = `r round(x_vs_y_summary$coefficients,4)[3,2]`, df = `r round(x_vs_y_summary$coefficients,4)[3,3]`, t = `r round(x_vs_y_summary$coefficients,4)[3,4]`, P = `r round(x_vs_y_summary$coefficients,4)[3,5]`).
We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B), (Main effect of age of horizontal position, B = `r round(x_pos_summary$coefficients,4)[2,1]`, SE = `r round(x_pos_summary$coefficients,4)[2,2]`, df = `r round(x_pos_summary$coefficients,4)[2,3]`, t = `r round(x_pos_summary$coefficients,4)[2,4]`, P = `r round(x_pos_summary$coefficients,4)[2,5]`; No main effect of age on vertical position, B = `r round(y_pos_summary$coefficients,4)[2,1]`, SE = `r round(y_pos_summary$coefficients,4)[2,2]`, df = `r round(y_pos_summary$coefficients,4)[2,3]`, t = `r round(y_pos_summary$coefficients,4)[2,4]`, P = `r round(y_pos_summary$coefficients,4)[2,5]`).

@@

An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Figure 4 and Appendix, Figure A8) and between individual children. 
Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 
This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. 
Each of these positions offer the child differing degrees of visual access to faces and hands. 
While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.
